{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-09-06 wacv_for_review.tex
Spell-Checking Performed

\usepackage{wacv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and extends amsmath package
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment, url}
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}
\newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}}

@@

\textbf{Kernelized Correlation Filter} The Kernelized Correlation
Filter is a well-known single target tracking method and its work
flow has been detailed in other papers
\cite{henriques2012exploiting,henriques2015high}. This section briefly
goes over the parts of the KCF relevant to this study. Its
computational efficiency is derived from the correlation filter
framework representing training examples as a circulant matrix. The
fact that a circulant matrix can be diagonalized by Discrete Fourier
transform is the key to reduce the complexity of any tracking method
based on correlation filter. The off-diagonal elements become zero
whereas the diagonal elements represent the eigenvalues of the
circulant matrix. The egienvalues are equal to the DFT transformation
of the base sample ($x$) elements. The Kernelized Correlation Filter,
in particular, applies a kernel to $x$ to transform to a more
discriminative domain. The circulant matrix is then formed by applying
cyclic shifts on the kernelized $x$. Such kernelization operation
maintains O($nlog(n)$) complexity unlike other kernel algorithms
leading to O($n^{2}$) or even higher complexities.

@@

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to the comparison with other tracking methods, we
also conducted an experiment to see what combination and deployment
order of the KCF work best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. For this experiment, we removed
the particle filter. The method at the $2^{nd}$ column fliped the
order of deploying $R_{t}^{L}$ and $R_{t}^{S}$ as presented at Figure
\ref{Workflows}. The one at the $3^{th}$ column removed $R_{t}^{S}$
and replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
removes $R_{t}^{L}$. The methods marked with ``*'' ran the filters on
every frame in the listed order. The methods at the $7^{th}$ and
$8^{th}$ columns ran a translation and a scale filter on every frame
which is very similar to the way the LCT tracker \cite{ma2015long}
runs. To be precise, the LCT tracker comes with a re-detection method
for a long-term tracking. In short, we empirically verified that
\textit{E}nKCF is an optimal way of using multiple KCFs, in terms of
tracking accuracy and run-time performance. For example, we could
achieve 4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$
at every frame, but this combination wills sacrifice run-time
performance, slowing down 317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$
and $R_{s}$ in every frame where $R_{t}^{S}$ uses the translation
estimated by $R_{t}^{L}$ to update translation and $R_{s}$ uses the
final translation estimation given by $R_{t}^{S}$ to update the scale.

\textbf{Evalution on Particle Filter Contribution} For the $UAV123$
dataset, we also evaluated the performance of the {\it E}nKCF with and
without the particle filter. In particular, we use 50 sequences
labeled as no abrupt camera motion in the dataset. To evaluate the
robustness of particle filter, we add noise, drawn from a uniform
distribution ($[-20,20]$), to the translation estimations of the
KCFs. In these setup, the {\it E}nKCF with particle filter achieves
$51.98\%$ precision ($20$px), outperforming the one without particle
filter {\it E}nKCF by $6.32\%$. Thus, with the removal of global
camera motion, the integration of particle filter into the {\it E}nKCF
as shown in Figure \ref{Workflows} further improved the results.

@@

Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows experimental
results of utilizing DNN features on UAV123 Dataset. Two settings of utilizing the deep
features outperformed the HoG and color features as proposed in {\it
  E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in
success rates (AUC). The \textit{conv224-VGG} setting performed
slightly better than \textit{conv222-VGG} in precision while achieving
similar success rate (AUC) indicating that higher level feature absraction
works better for the smaller ROIs.
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.40cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's ({\it hog} + {\it color}) performance with Deep{\it E}nKCF on the UAV123
dataset.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}

>>>>

\usepackage{wacv}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools} % mathtools builds on and exten0))ds amsmath package
\usepackage{algpseudocode}	% http://ctan.org/pkg/algorithmicx% Include other packages here, before hyperref.
\usepackage{comment, url}
\usepackage[ruled, vlined, linesnumbered]{algorithm2e}
\newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}}

@@

\textbf{Kernelized Correlation Filter} The Kernelized Correlation
Filter is a well-known single target tracking method and its work
flow has been detailed in other papers
\cite{henriques2012exploiting,henriques2015high}. This section briefly
goes over the parts of the KCF relevant to this study. Its
computational efficiency is derived from the correlation filter
framework representing training examples as a circulant matrix. The
fact that a circulant matrix can be diagonalized by Discrete Fourier
transform is the key to reduce the complexity of any tracking method
based on correlation filter. The off-diagonal elements become zero
whereas the diagonal elements represent the eigenvalues of the
circulant matrix. The eigenvalues are equal to the DFT transformation
of the base sample ($x$) elements. The Kernelized Correlation Filter,
in particular, applies a kernel to $x$ to transform to a more
discriminative domain. The circulant matrix is then formed by applying
cyclic shifts on the kernelized $x$. Such kernelization operation
maintains O($nlog(n)$) complexity unlike other kernel algorithms
leading to O($n^{2}$) or even higher complexities.

@@

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to the comparison with other tracking methods, we
also conducted an experiment to see what combination and deployment
order of the KCF work best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. For this experiment, we removed
the particle filter. The method at the $2^{nd}$ column flipped the
order of deploying $R_{t}^{L}$ and $R_{t}^{S}$ as presented at Figure
\ref{Workflows}. The one at the $3^{th}$ column removed $R_{t}^{S}$
and replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
removes $R_{t}^{L}$. The methods marked with ``*'' ran the filters on
every frame in the listed order. The methods at the $7^{th}$ and
$8^{th}$ columns ran a translation and a scale filter on every frame
which is very similar to the way the LCT tracker \cite{ma2015long}
runs. To be precise, the LCT tracker comes with a re-detection method
for a long-term tracking. In short, we empirically verified that
\textit{E}nKCF is an optimal way of using multiple KCFs, in terms of
tracking accuracy and run-time performance. For example, we could
achieve 4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$
at every frame, but this combination wills sacrifice run-time
performance, slowing down 317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$
and $R_{s}$ in every frame where $R_{t}^{S}$ uses the translation
estimated by $R_{t}^{L}$ to update translation and $R_{s}$ uses the
final translation estimation given by $R_{t}^{S}$ to update the scale.

\textbf{Evaluation on Particle Filter Contribution} For the $UAV123$
dataset, we also evaluated the performance of the {\it E}nKCF with and
without the particle filter. In particular, we use 50 sequences
labeled as no abrupt camera motion in the dataset. To evaluate the
robustness of particle filter, we add noise, drawn from a uniform
distribution ($[-20,20]$), to the translation estimations of the
KCFs. In these setup, the {\it E}nKCF with particle filter achieves
$51.98\%$ precision ($20$px), outperforming the one without particle
filter {\it E}nKCF by $6.32\%$. Thus, with the removal of global
camera motion, the integration of particle filter into the {\it E}nKCF
as shown in Figure \ref{Workflows} further improved the results.

@@

Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows experimental
results of utilizing DNN features on UAV123 Dataset. Two settings of utilizing the deep
features outperformed the HoG and color features as proposed in {\it
  E}nKCF by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in
success rates (AUC). The \textit{conv224-VGG} setting performed
slightly better than \textit{conv222-VGG} in precision while achieving
similar success rate (AUC) indicating that higher level feature abstraction
works better for the smaller ROIs.
\begin{figure}[!h]
\centering
\begin{tabular}{ccc}
\tiny\quad\quad\textbf{UAV123}\\
\includegraphics[width=3.30cm]{./figures/pr_deep.eps}
\includegraphics[width=3.40cm]{./figures/sr_deep.eps}\\
\end{tabular}
\caption{Comparison of {\it E}nKCF's ({\it hog} + {\it color}) performance with Deep{\it E}nKCF on the UAV123
dataset.}
\label{fig:UAV123_DATASET_DeepFeatures}
\end{figure}
